TSELM: Target speaker extraction using discrete tokens and language models \thanks{Our demos are available at: }

### 2024-09-06 src/paper.tex
update

\title{TSELM: Target speaker extraction using discrete tokens and language models
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}
We present TSELM, a novel target speaker extraction network using discrete tokens and language models. This model utilizes multiple discretized layers
of WavLM Large as input tokens. It uses cross attention to inject target speaker information and language models to model the sequences. 
\end{abstract}

>>>>

\title{TSELM: Target speaker extraction using discrete tokens and language models
\thanks{Our demos are available at: }
}

@@

\begin{abstract}
We present TSELM, a novel target speaker extraction network using discrete tokens and language models. This model utilizes multiple discretized layers
of WavLM Large as input tokens. It uses cross attention to inject target speaker information and language models to model the sequences. It uses 
a scalable HiFi-GAN to reconstruct the audio from the tokens. It uses 
cross entropy loss to model the probability of output tokens, transforming the complex regression problems into classification problems. To the best of our 
knowledge, we are the first to do target speaker extraction using discrete tokens. However, there is still a gap between our model and continuous methods. 
Our codes and pretrained models are available at: .
\end{abstract}
